---
title: "Palmerpenguins Data Viz"
author: "Yevhen"
date: "2024-11-28"
output: html_document
---


### Setting up my environment 
Notes: setting up my R environment by loading the 'tidyverse' and 'palmerpenguins, 'DT' packages

```{r ggplot for penguin data}
library(ggplot2)
library(palmerpenguins)
library(DT)
```
### Importing a small part of data

```{r data exploring}
data(penguins)
datatable(penguins)
```

### Visualisations
Here we will go through a serious of visualisations 

#### Flipper and body mass in purple 
Here, we plot flipper length against body mass 

```{r visualise flipper and body mass in purple}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +  geom_point(color="purple")
```

#### Flipper and body mass by species
Here, we plot flipper length against body mass and look at the breakdown by species

```{r visualise flipper and body mass by species}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) + 
  geom_point(aes(shape=species))
```

#### Flipper and body mass by species and sex
Here, we plot flipper length against body mass and look at the breakdown by species

```{r species and sex}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +   geom_point(aes(color=species,
  shape=species)) +
    facet_wrap(~sex)
```
